Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-17 reanalysis-3-propensity_scores.qmd
bugfix

  # Store results
  twang_results[[i]] <- list(
    model = twang_model,
    weights = weights,
    ps_scores = twang_model$ps[, "es.mean"],
    n_trees_used = twang_model$desc$es.mean$n.trees,
    balance_es_mean = twang_model$balance$es.mean
  )

@@

  # Summary statistics for es.mean method
  balance_summaries[[i]] <- data.frame(
    Imputation = i,
    Mean_ES = mean(abs(bal_es$std.eff.sz), na.rm = TRUE),
    Max_ES = max(abs(bal_es$std.eff.sz), na.rm = TRUE),
    N_Imbalanced = sum(abs(bal_es$std.eff.sz) > 0.1, na.rm = TRUE),
    # KS statistics are still available in the es.mean balance table
    Mean_KS = mean(bal_es$ks, na.rm = TRUE),
    Max_KS = max(bal_es$ks, na.rm = TRUE)
  )
}

>>>>

  # Store results
  # When using single stop method, ps is a vector not a matrix
  ps_scores <- if(is.matrix(twang_model$ps)) {
    twang_model$ps[, "es.mean"]
  } else {
    twang_model$ps  # Already a vector when single stop method
  }

  twang_results[[i]] <- list(
    model = twang_model,
    weights = weights,
    ps_scores = ps_scores,
    n_trees_used = twang_model$desc$es.mean$n.trees,
    balance_es_mean = bal.table(twang_model, type = "es.mean")
  )

@@

  # Extract standardized effect sizes and KS statistics
  # The balance table structure may vary, so check column names
  if ("std.eff.sz" %in% names(bal_es)) {
    std_eff_col <- "std.eff.sz"
  } else if ("std.es" %in% names(bal_es)) {
    std_eff_col <- "std.es"
  } else {
    # Find column with "std" in name
    std_cols <- grep("std", names(bal_es), value = TRUE)
    std_eff_col <- std_cols[1]
  }

  if ("ks" %in% names(bal_es)) {
    ks_col <- "ks"
  } else if ("ks.max" %in% names(bal_es)) {
    ks_col <- "ks.max"
  } else {
    # Find column with "ks" in name
    ks_cols <- grep("ks", names(bal_es), value = TRUE)
    ks_col <- if(length(ks_cols) > 0) ks_cols[1] else NULL
  }

  # Summary statistics for es.mean method
  balance_summaries[[i]] <- data.frame(
    Imputation = i,
    Mean_ES = mean(abs(bal_es[[std_eff_col]]), na.rm = TRUE),
    Max_ES = max(abs(bal_es[[std_eff_col]]), na.rm = TRUE),
    N_Imbalanced = sum(abs(bal_es[[std_eff_col]]) > 0.1, na.rm = TRUE),
    # KS statistics if available
    Mean_KS = if(!is.null(ks_col)) mean(bal_es[[ks_col]], na.rm = TRUE) else NA,
    Max_KS = if(!is.null(ks_col)) max(bal_es[[ks_col]], na.rm = TRUE) else NA
  )
}
